Non-Vertical Cultural Transmission, Assortment, \\and the Evolution of Cooperation

### 2020-09-07 ms/main.tex
Start using social association term instead of meeting assortment

\begin{corollary}[Perfect assortment of transmission and cooperation]
With perfect assortment ($\alpha=1$), there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found from inequality \ref{eq:vert_hori_alpha1_condition_proof}, namely
\begin{equation}\label{eq:vert_hori_alpha1}
c < \frac{b \cdot T_A + (T_A - T_B)}{1-T_B}.
\end{equation}
\end{corollary}
With perfect assortment horizontal transmission always co-occurs with the cooperative interaction. The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).

@@

Given the previous two corollaries for no assortment and perfect assortment ($\alpha=0$ and $\alpha=1$), it is interesting to examine the general effect of assortment on the evolution of cooperation.
We denote the assortment boundaries by
\begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting}
  a_1 = \frac{c(1-T_B)-(1+b)(T_A-T_B)}{b\cdot T_B}, \quad
  a_2 = \frac{c(1-T_B)-(T_A-T_B)}{b\cdot T_A}.
\end{aligned}\end{equation}
Applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we have the following corollary.
\\

@@

    \includegraphics[scale=0.75]{boundiries_withAlpha_y_axis.pdf}
    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
(\textbf{a-b})~the cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
(\textbf{c})~the assortment $\alpha$ is on the y-axis; the assortment boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
  % TODO missing text descriptions of conditions on (3)
  	}
    \label{fig:results2}
\end{figure}

>>>>

\begin{corollary}[Perfect assortment of transmission and cooperation]
With perfect assortment ($\alpha=1$), there are only two equilibria, $\tilde{p}=0$ and $\tilde{p}=1$.
The condition for evolution of cooperation (i.e. global stability of $\tilde{p}=1$) is found from inequality \ref{eq:vert_hori_alpha1_condition_proof}, namely
\begin{equation}\label{eq:vert_hori_alpha1}
c < \frac{b \cdot T_A + (T_A - T_B)}{1-T_B}.
\end{equation}
\end{corollary}
With perfect social association horizontal transmission always co-occurs with the cooperative interaction. The same occurs in \citet{lewin2017microbes}, and therefore this corollary is equivalent to their result (see their eq.~1).

@@

Given the previous two corollaries for no association and perfect association ($\alpha=0$ and $\alpha=1$), it is interesting to examine the general effect of social association on the evolution of cooperation.
We denote the social association boundaries by
\begin{equation}\begin{aligned}\label{eq:boundries_assortative_meeting}
  a_1 = \frac{c(1-T_B)-(1+b)(T_A-T_B)}{b\cdot T_B}, \quad
  a_2 = \frac{c(1-T_B)-(T_A-T_B)}{b\cdot T_A}.
\end{aligned}\end{equation}
Applying Eqs.~\ref{eq:vert_hori_equilibrium}, \ref{eq:vert_hori_global_condition1}, and \ref{eq:vert_hori_global_condition2}, we have the following corollary.
\\

@@

    \includegraphics[scale=0.75]{boundiries_withAlpha_y_axis.pdf}
    \caption{\textbf{Evolution of cooperation under vertical and horizontal cultural transmission.} 
The figure shows the global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial conditions, i.e. unstable coexistence (blue), and stable coexistence of cooperation and defection (yellow).
In all cases the horizontal bias ($T_A-T_B$) is on the x-axis.
(\textbf{a-b})~the cost of cooperation $c$ is on the y-axis; the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}) are the solid and dashed lines. 
(\textbf{c})~the social association $\alpha$ is on the y-axis; the social association boundaries $a_1$ and $a_2$ (\autoref{eq:boundries_assortative_meeting}) are the solid and dashed lines.
Here, $b=1.3$, $T_A=0.4$. (\textbf{a})~$\alpha = 0$.(\textbf{b})~$\alpha = 0.7$. (\textbf{c})~$c = 0.35$.
  % TODO missing text descriptions of conditions on (3)
  	}
    \label{fig:results2}
\end{figure}
